### 2015-12-10 paper/4-performance.tex
Added a bit of explanation on PHOLD already

\subsubsection{PHold}
In the Phold model, we first investigate the influence of the fraction of remote events.
%TODO wait for results
%The dynamic dependency graph is a very sparse version of the static dependency graph, penalizing the conservative case. The lookahead is $\epsilon$, so the conservative case spends most of its time crawling in steps of $\epsilon$. Since the dependency graph between kernels is a complete graph, this is not a simulation that scales in our implementation. For $N$ kernels, each kernel has to query the null-time of $N-1$ kernels, resulting in O($N^2$) polling behaviour. In a non-cyclic simulation with a non-trivial lookahead (like in, e.g., Devstone), that choice does pay off (see Figure~\ref{fig:DevstoneParallel}). Adevs's lesser performance is due in part to their lookahead management, which after profiling shows to spend a non-trivial amount of time in exception handling code.\\
%The optimistic case suffers little from the above problems; due to the high interconnectivity, however, a cascading revert is still possible. With the percentage of remotes equal to $100$, Phold reflects interconnect in behaviour, which is why the $R$ value is not dimensioned here. A revert is very expensive in PHold due to our usage of C++11's random nr generators. The cost of a revert is dominated by the recalculation of destination models, not in allocating/deallocating states/messages. Once a revert happens the drift between kernels increases fast, increasing the likelihood of more reverts. Despite all this, optimistic can for low $R$ values quickly exploit the uncertainty that slows down conservative in this benchmark.

>>>>

\subsubsection{PHold}
In the Phold model, we first investigate the influence of the fraction of remote events on the speedup.
When remote events are rare, optimistic synchronization will also have rare rollbacks, thus increasing performance.
With more common remote events, however, optimistic synchronization quickly loses its advantage due to the more frequent rollbacks.
Conservative synchronization, on the other hand, is largely unconcerned with the number of remote events: the mere fact that a remote event can happen, causes it to block.
Even though a single synchronization protocol suffices in this case, it shows how different synchronization protocols respond differently to a changing model.
Adevs, on the other hand, is significantly slower during conservative synchronization.
Analysis of profiling results shows that this was caused by exception handling within the adevs simulation kernel.
